---
title: "p8105_hw6_yz4437.Rmd"
author: "Yuchen Zhang"
date: "2022-12-01"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 



##Problem 2

Import and clean. Create a `city_state` variable, create a binary variable `resolved` indicate whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Limit data to whom victim_race is white or black and victim_age is numeric.
```{r}
homicide_data = read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolved = as.numeric(disposition == "Closed by arrest")
  )%>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO","Tulsa, AL"))) %>%
  filter(victim_race %in% c("White", "Black"), victim_age != "Unknown") %>% 
  mutate(
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")
    )
```
For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object.
```{r}
Baltimore_logistic = 
  homicide_data %>%
  filter(city == "Baltimore") %>% 
  select(city_state, resolved, victim_age, victim_race, victim_sex) %>%
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 

#save as an R object
save(Baltimore_logistic, file = "results/Baltimore_logistic.RData")

Baltimore_logistic
```

Apply the broom::tidy to this object and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
```{r}
Baltimore_logistic %>% 
  broom::tidy()%>% 
  mutate(lower_conf = confint(Baltimore_logistic)[,1],
         upper_conf = confint(Baltimore_logistic)[,2]) %>% 
  filter(term =='victim_sexMale') %>% 
  mutate(OR = exp(estimate),
         lower_conf = exp(lower_conf),
         upper_conf = exp(upper_conf)) %>% 
  select(OR, lower_conf, upper_conf)
```

run glm for each of the cities and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. create a dataframe with estimated ORs and CIs for each city.
```{r}
cities_df = 
  homicide_data %>% 
  select(city_state, victim_race:victim_sex, resolved) %>% 
  nest(data = victim_race:resolved) %>% 
  mutate(
    models = map(data, ~glm(resolved ~ victim_age+victim_race+victim_sex, family= binomial(), data=.x)),
    results = map(models, broom::tidy),
    conf_int = map(models, ~confint(.x,"victim_sexMale"))
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  unnest_wider(conf_int) %>% 
  filter(term == 'victim_sexMale') %>% 
  select(city_state,estimate,`2.5 %`,`97.5 %`) %>% 
  #convert to odds scale
  mutate(
    OR = exp(estimate),
    lower_bound = exp(`2.5 %`),
    upper_bound = exp(`97.5 %`)
    ) %>% 
  select(city_state,OR,lower_bound,upper_bound)
```
Create a plot that shows the estimated ORs and CIs for each city
```{r}
cities_df %>% 
ggplot(aes(x = fct_reorder(city_state, OR), y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_bound, ymax= upper_bound))+
  labs(title = "Estimated ORs and CIs for each city", caption = "95% confidence interval", x = "City, State")  +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
From the plot, most of the cities have an odd ratio less than one, this means that men have fewer solved homicides than women. New York has lowest odd ratio and Albuquerque have highest odd ratio. The confident interval of Albuquerque, San Bernardino, Fresno and Stockton are large, so the estimate odd ratio may not very reliable.

##Problem 3

Load and clean the data for regression analysis
```{r}
birthweight = read_csv("data/birthweight.csv", show_col_types = FALSE)
birthweight
```


```{r}
birthweight = birthweight %>% 
  mutate(across(c(babysex, frace, malform, mrace), as.factor)) %>% 
  select(bwt, everything()) 

birthweight = na.omit(birthweight)
sum(is.na(birthweight))
```

```{r}
full = lm(bwt ~ ., data = birthweight)
```

Plot of model residuals against fitted values:

```{r}
birthweight %>% 
  add_predictions(full) %>% 
  add_residuals(full) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .5)
```


```{r, warning=FALSE}
cv_df =
  crossv_mc(birthweight, 100)
```



```{r, warning=FALSE}
cv_df = 
  cv_df %>% 
mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
#then fit three models:
cv_df = 
  cv_df %>% 
  mutate(
    my_model  = map(train, ~full),
    main_effect_model  = map(train, ~lm(bwt ~ gaweeks + blength, data = .x)),
    interactive_model  = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))) %>% 
  mutate(
    rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_main_effect= map2_dbl(main_effect_model, test, ~rmse(model = .x, data = .y)),
    rmse_interactive = map2_dbl(interactive_model, test, ~rmse(model = .x, data = .y)))
#Get the summarize the result:
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
